Classifying Protein Secondary Structures through Deep Network Learning

### 2013-12-18 docs/paper.tex
Fix latex bugs

\subsection{Deep Networks}
The final deep network has a window size of 13, and 6 hidden layers of size 26.
Its accuracy is ___\%.

% FIXME how ROC curve created
We created ROC curves to measure the performance of the deep network.
Confidence was calculated by subtracting the output values for the two losing nodes from the winning output values.
Because there are multiple classifications, we can't use the basic 2-classification ROC curve format.
Instead, we chose to use a one-versus-many ROC curve, which shows the false positive and true positive rates for each class.

@@

\subsection{Ensembles}
Our best deep network performs signifcantly worse than the baseline neural network, so a natural modification is to try using ensembles of networks.
Since deep networks require significant time complexity, we were unable to train an ensemble of deep networks.
However, we were able to train an ensemble of simple neural networks with one hidden layer.
%Figure \ref{fig:baseline_ensemble} shows that 
An ensemble of three neural networks has an average accuracy of 61.65\%.
The best baseline neural network settings, as discussed in section ______,  produced an average accuracy of 59.51\%, which is two percentage points lower than the ensemble.
So, using an ensemble clearly improves the performance of the baseline network, and we hypothesize that deep networks would also benefit from this technique.

@@

% describe results
% Insert and discuss ROC curves -- should I put ALPHA, BETA, LOOP on one plot?
% combine into 1????
\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ensemble/ROC_ALPHA.png}
\caption{}
\label{fig:roc_alpha}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ensemble/ROC_BETA.png}
\caption{}
\label{fig:roc_beta}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ensemble/ROC_LOOP.png}
\caption{}
\label{fig:roc_loop}
\end{figure}

>>>>

\subsection{Deep Networks}
The final deep network has a window size of 13, and 6 hidden layers of size 26.
Its accuracy is %___\%. FIXME

We created ROC curves to measure the performance of the deep network.
Confidence was calculated by subtracting the output values for the two losing nodes from the winning output values.
Because there are multiple classifications, we can't use the basic 2-classification ROC curve format.
Instead, we chose to use a one-versus-many ROC curve, which shows the false positive and true positive rates for each class.

@@

\subsection{Ensembles}
Our best deep network performs signifcantly worse than the baseline neural network, so a natural modification is to try using ensembles of networks.
Since deep networks require significant time complexity, we were unable to train an ensemble of deep networks.
However, we were able to train an ensemble of simple neural networks with one hidden layer.
%Figure \ref{fig:baseline_ensemble} shows that 
An ensemble of three neural networks has an average accuracy of 61.65\%.
The best baseline neural network settings, as discussed in section %______, FIXME
produced an average accuracy of 59.51\%, which is two percentage points lower than the ensemble.
So, using an ensemble clearly improves the performance of the baseline network, and we hypothesize that deep networks would also benefit from this technique.

@@

% describe results
% Insert and discuss ROC curves -- should I put ALPHA, BETA, LOOP on one plot?
% combine into 1????
\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ROC_ALPHA.png}
\caption{}
\label{fig:roc_alpha}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ROC_BETA.png}
\caption{}
\label{fig:roc_beta}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=65mm]{results/ROC_LOOP.png}
\caption{}
\label{fig:roc_loop}
\end{figure}
